---
title: "Lab2"
author: "Tess"
output: 
  pdf_document: 
---

```{r setup, include=FALSE}
#Ignore this code chunk for now. 
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

Run the following code to 
  (a) install the {nlme} and {janitor} packages
  (b) load the packages along with the tidyverse, and
  (c) access and quickly prep some data (from the {nmle} package) for plotting.

```{r eval=FALSE}
# Note: You only need to run this next line one time to install these two packages.
install.packages(c("nlme", "janitor"))
```


```{r data-download}

library(nlme) 
library(janitor) 
library(tidyverse) 

pd <- Oxboys %>% 
  clean_names() %>% 
  mutate(subject = factor(subject),
         occasion = factor(occasion)) %>% 
  filter(subject == "10" | subject == "4" | subject == "7") %>% 
  tbl_df()
```

1. Reproduce the following two plots, using the *pd* data. You can use whatever theme you want (I used `theme_minimal()`), but all else should be the same. 


```{r plots1, message = FALSE, warning = FALSE}

# Put code below for Plot 1. Note that Plot 1 is a line plot, not a smooth.

ggplot(pd, aes(age, height)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~subject) +
  ggtitle("Plot1")




# Put code below for Plot 2. Note that Plot 2 is a line plot also.

ggplot(pd, aes(age, height)) +
  geom_line(aes(color = subject)) +
  ggtitle("Plot2")
 

```

\newpage

2. Use the *mtcars* dataset from base R to replicate the following plots. (Just type *mtcars* into the console to see the dataset).

```{r plots2}

# Put code below for Plot 3

ggplot(mtcars, aes(drat, mpg)) +
  geom_point() +
  ggtitle("Plot3")


# Put code below for Plot 4

ggplot(mtcars, aes(drat, mpg)) +
  geom_point() +
  geom_smooth() +
  ggtitle("Plot4")


# Put code below for Plot 5

ggplot(mtcars, aes(drat, mpg)) +
  geom_point() +
  stat_smooth(method = "lm", formula = y ~ x, size = 1) +
  facet_wrap(~vs) +
  ggtitle("Plot5")

# Put code below for Plot 6. I have given you the first line of code to start.
ggplot(mtcars, aes(drat, mpg, color = factor(cyl))) +
  geom_point() + 
  geom_smooth(method = "lm", se = F) +
 ggtitle("Plot6")
  


```

\newpage

3. Use the *Orange* dataset, also part of base R, to replicate the following plots.
   
```{r orange-plots}
# Put code below for Plot 7

ggplot(Orange, aes(age, circumference, color = Tree)) +
  coord_cartesian(xlim = c(300, 1650), ylim = c(25, 225)) +
  geom_point() +
  geom_smooth(se = F) +
  ggtitle("Plot7")

# Put code below for the last plot. See slide 51 from the w2p2 class for labels.
ggplot(Orange, aes(age, circumference)) +
  coord_cartesian(xlim = c(300, 1650), ylim = c(25, 225)) +
  geom_point(aes(color = Tree)) +
  geom_smooth(method = "lm", se = F, color = "gray48") +
  ggtitle("Orange Tree Growth \nGray line displays a linear model fit to the data") +
  xlab("Age of the Tree (in days)") +
  ylab("Circumference of the Trunk (in mm)")



```
