---
title: "Lab 3"
author: "Tess"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

1. Run the following code to load the *tidyverse*.

```{r load-tidyverse}
library(tidyverse)
```

1. Run the following lines of code to view and read about the data we'll use 
for this lab. 

Comment out line 26 after you run it, but puting a `#` at the start.

```{r gsscat, eval = FALSE}
#str(gss_cat)
View(gss_cat)
?gss_cat 
```

2. Use `ggplot` to create a histogram of `tvhours`. The plot should:
  + Include a small amount of transparency so gridlines are visible under the 
    histogram.
  + Be a different color than the default
  + Include meaningful axis labels
  + Have a title and a subtitle

```{r question-2}
ggplot(gss_cat, aes(x = tvhours)) +
  geom_histogram(alpha = 0.7, color = "cornflowerblue") +
  ggtitle("Number of TV hours watched \r\nBy a largly white demographic") +
  xlab("Hours watching TV") +
  ylab("Number of People") 
  
  



```

3. Create a ridgeline density plot of `age` by `partyid`. Do you notice any strong
  differences by party affiliation?

```{r question-3}
#install.packages("ggridges")
library(ggridges)

ggplot(gss_cat, aes(x = age, y = partyid)) +
  geom_density_ridges()

#Generally middle aged people seem to not want to disclose their affiliation or have strong support for their party. Younder ages seem to show less affinity for ether party.

```

4. Modify the plot from Question 3 to produce separate ridgeline densities by `race`. Do you see any patterns?

```{r question-4}

ggplot(gss_cat, aes(x = age, y = race)) +
  geom_density_ridges()

#Yes but given the lack of black and other participant numbers its hard to conclude anything besides this data set has alot of white participants and alot of younger people from the other demographic   

```

5. Replicate the plots from Questions 3 and 4, but this time displaying the relations with boxplots (i.e., one boxplot from Question 3 and one boxplot for Question 4 in the chunk below). Which do you think displays the relation more clearly? Why?
  
```{r label, options}
#Q3 boxplot
ggplot(gss_cat, aes(x = age, y = partyid)) +
  geom_boxplot() 

#Q4 boxplot
ggplot(gss_cat, aes(x = age, y = race)) +
  geom_boxplot()

#the box plots are clearer since you can distinguish the mean value and the distribution more easily 
```

6. Run the following lines of code to get a correlation table as a data frame.

```{r corr-mat-df}
# You might need to install the ISLR package using the line below. 
# If so, uncomment out the line, install the pacakge, then comment the line again. 
# Your document won't knit if you do not comment the line below.

#install.packages("ISLR") 
library(ISLR)
cor_tbl <- Hitters %>% 
  select_if(is.numeric) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  as.data.frame() %>% 
  mutate(row = row.names(.)) %>% 
  pivot_longer(
    cols = -row,
    names_to = "col",
    values_to = "cor"
  ) %>% 
  tbl_df()
```

Use the correlation table to create a heatmap using `geom_tile`. Change the 
colors to one of the four viridis palettes. What does the heatmap help you see?

```{r, heatmap}
ggplot(cor_tbl, aes(row, col, fill = cor))+
  geom_tile() +
  scale_fill_viridis_c()

#That theres a high correlation between some of the values, but i dont know enough about baseball to see it 
  
```

7. The code below will produce a barplot. 

```{r barplot1}
ggplot(gss_cat, aes(rincome)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Use the code below to create a new data set - `gss_cat_new` - that redefines the `rincome` variable so that *Not applicable* is displayed first, followed by *No answer*, *Don't know*, *Refused*, and then each income category from lowest to highest. Once you've redefined the factor variable, re-produce the plot above by running the `ggplot` code at the bottom of the chunk. The plot should have *Not applicable* closest to the y-axis, then *No answer*, *Don't know*, etc.

```{r redfine-factor, echo = FALSE}
gss_cat_new <- gss_cat %>% 
  mutate(rincome = factor(rincome, levels = c("Not applicable", "No answer", "Don't know", "Refused", "Lt $1000", "$1000 to 2999", "$3000 to 3999", "$4000 to 4999", "$5000 to 5999", "$6000 to 6999", "$7000 to 7999",  "$8000 to 9999", "$10000 - 14999", "$15000 - 19999", "$20000 - 24999")))

ggplot(gss_cat_new, aes(rincome)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```