---
title: "Lab 4"
author: "Your Name Here"
date: "October 14, 2020"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
 knitr::opts_chunk$set(message = FALSE, 
                       warning = FALSE)
```


Install and load the package *Lahman*, which will give you access to the dataset *Teams*

```{r teams_echo, echo = TRUE}
#install.packages("Lahman")
library(Lahman)
library(tidyverse)
library(janitor)
```
* Produce a subset of the data (as a new object) that has the following characteristics:
    + Only one team (your choice)
    + data from 1980 to present (or as present as the dataset gets)
    + Includes 5 columns: name, yearID, W, L, R, RA

(The variables above correspond to the team name, the year, wins, losses, runs scored, and runs allowed)

* Make sure you select a team that is currently still around, or it probably
won't be interesting (see a list of current at [http://www.espn.com/mlb/teams](http://www.espn.com/mlb/teams)).

* Create a new variable corresponding to the winning percentage for the team 
  you chose over time

$$w_{pct} = \frac{wins}{wins + losses}$$

* Order by winning percentage: Least to greatest
* Order by winning percentage: greatest to least
* Compute the mean and standard deviation of winning percentage
* With the full dataset
  + compute the average and standard deviation of winning percentage for each team. 
  + Order by highest winning percentage
* Use the full data to reproduce the plot below

```{r answers}
NYG <- 
  Teams %>% 
    select(name, yearID, W, L, R, RA) %>% 
      filter(name == "New York Giants")  %>% 
        mutate(w_pct = (W)/(W + L))

NYG_w_asc <- NYG %>% 
  arrange(w_pct)

view(NYG_w_asc) 

NYG_w_des <- NYG %>% 
  arrange(desc(w_pct))

NYG %>% summarize(mean_w_pct = mean(w_pct),
                  sd_w_pct = sd(w_pct))

Teams_w_pct <- 
  Teams %>% 
    select(name, yearID, W, L, R, RA) %>% 
      group_by(name)  %>% 
        mutate(w_pct = (W)/(W + L)) %>% 
          arrange(desc(w_pct))



          

```


```{r plot}
# Please put the code for the plot in this chunk.
Teams_w_pct %>% 
  group_by(name) %>% 
  summarize(mean_w_pct = mean(w_pct),
            sd_w_pct = sd(w_pct)) %>% 
    filter(name == "New York Yankees" & 
           name == "Detroit Tigers" &
           name == "San Diego Padres") %>% 
              ggplot(aes(yearID, w_pct, color = name)) +
                geom_line()
  


```
